\pkg{NeuralNetTools}: Visualization and Analysis Tools for Neural Networks

### 2018-05-03 nnt_manu.Rnw
working on final JSS edits

# other libs
library("ggplot2")
@
% get online bib file
<<echo = FALSE>>=
refs <- httr::GET('https://raw.githubusercontent.com/fawda123/refs/master/refs.bib')
refs <- rawToChar(refs$content)
writeLines(refs, con = file('refs.bib'))
@

@@

# subet by nodes so barplots can be ordered by medians
toplo1 <- filter(imp_sums, nodes == 1) %>% 
  mutate(variable = factor(variable, levels = levels(variable)[order(med)]))
toplo2 <- filter(imp_sums, nodes == 5) %>% 
  mutate(variable = factor(variable, levels = levels(variable)[order(med)]))
toplo3 <- filter(imp_sums, nodes == 10) %>% 
  mutate(variable = factor(variable, levels = levels(variable)[order(med)]))

# widths
wd <- 0.3
ylims <- c(-3.93, 3.49)

@@

% note that ref titles need to be in title-case 
% \bibliographystyle{jss}
% \bibliography{refs}
% this file is bbl edited by hand after running bibtex
\input{CopyOfnnt_manu.bbl}

>>>>

# other libs
library("ggplot2")
@

@@

# subet by nodes so barplots can be ordered by medians
toplo1 <- filter(imp_sums, nodes == 1) %>% 
  mutate(variable = factor(variable, levels = variable[order(med)]))
toplo2 <- filter(imp_sums, nodes == 5) %>% 
  mutate(variable = factor(variable, levels = variable[order(med)]))
toplo3 <- filter(imp_sums, nodes == 10) %>% 
  mutate(variable = factor(variable, levels = variable[order(med)]))

# widths
wd <- 0.3
ylims <- with(imp_sums, c(min(lo), max(hi)))

@@

% note that ref titles need to be in title-case 
% \bibliographystyle{jss}
\bibliography{refs}

### 2018-05-03 nnt_manu.tex
working on final JSS edits

% options and libs
% get online bib file

@@

Methods in \pkg{NeuralNetTools} were written for several \proglang{R} packages that can be used to create \ac{mlp} neural networks: \pkg{neuralnet} \citep{Fritsch12}, \pkg{nnet} \citep{Venables02}, and \pkg{RSNNS} \citep{Bergmeir12}. Limited methods were also developed for neural network objects created with the \code{train} function from the \pkg{caret} package \citep{Kuhn15}.  Additional \proglang{R} packages that can create \ac{mlp} neural networks include \pkg{AMORE} that implements the `TAO-robust backpropagation algorithm' for model fitting \citep{Castejon14}, \pkg{FCNN4R} as an \proglang{R} interface to the \pkg{FCNN} \proglang{C++} library \citep{Klima15}, \pkg{monmlp} for networks with partial monotonicity constraints \citep{Cannon15}, and \pkg{qrnn} for quantile regression neural networks \citep{Cannon11}.  At the time of writing, the \ac{CRAN} download logs \citep{Csardi15} showed that the \proglang{R} packages with methods in \pkg{NeuralNetTools} included 95\% of all downloads for the available \ac{mlp} packages, with \pkg{nnet} accounting for over 78\%.  As such, methods have not been included in \pkg{NeuralNetTools} for the remaining packages, although further development of \pkg{NeuralNetTools} could include additional methods based on popularity.  Methods for each function are currently available for  \code{mlp} (\pkg{RSNNS}), \code{nn} (\pkg{neuralnet}), \code{nnet} (\pkg{nnet}), and \code{train} (\pkg{caret}, only if the object also inherits from the \code{nnet} class).  Additional \code{default} or \code{numeric} methods are available for some of the generic functions.

>>>>

% options and libs

@@

Methods in \pkg{NeuralNetTools} were written for several \proglang{R} packages that can be used to create \ac{mlp} neural networks: \pkg{neuralnet} \citep{Fritsch12}, \pkg{nnet} \citep{Venables02}, and \pkg{RSNNS} \citep{Bergmeir12}. Limited methods were also developed for neural network objects created with the \code{train} function from the \pkg{caret} package \citep{Kuhn15}.  Additional \proglang{R} packages that can create \ac{mlp} neural networks include \pkg{AMORE} that implements the `TAO-robust backpropagation algorithm' for model fitting \citep{Castejon14}, \pkg{FCNN4R} as an \proglang{R} interface to the \pkg{FCNN} \proglang{C++} library \citep{Klima15}, \pkg{monmlp} for networks with partial monotonicity constraints \citep{Cannon15}, and \pkg{qrnn} for quantile regression neural networks \citep{Cannon11}.  At the time of writing, the \ac{CRAN} download logs \citep{Csardi15} showed that the \proglang{R} packages with methods in \pkg{NeuralNetTools} included 95\% of all downloads for the available \ac{mlp} packages, with \pkg{nnet} accounting for over 68\%.  As such, methods have not been included in \pkg{NeuralNetTools} for the remaining packages, although further development of \pkg{NeuralNetTools} could include additional methods based on popularity.  Methods for each function are currently available for  \code{mlp} (\pkg{RSNNS}), \code{nn} (\pkg{neuralnet}), \code{nnet} (\pkg{nnet}), and \code{train} (\pkg{caret}, only if the object also inherits from the \code{nnet} class).  Additional \code{default} or \code{numeric} methods are available for some of the generic functions.
